To Do List

### 2018-09-11 ToDo.Rmd
new todo

* Should we use elastic-net and RF as final models or just one or the other?
* In results section should we compare between mourad models visually or verbally or none at all?
* I've mentioned other methods in intro, it will be hard to compare to the others; how to handle this?
* Hong et al uses TFBS should I also include them?

@@

*Finish Methods
*Finish running code applied to 100 iterations of undersampling
*Apply pipeline to K562 cell line

>>>>

* Should we use elastic-net and RF as final models or just one or the other?
* In results section should we compare between mourad models visually or verbally or none at all?
   + visually and verbally
   + AUROCs, F1 and MCC
* I've mentioned other methods in intro, it will be hard to compare to the others; how to handle this?
* Hong et al uses TFBS should I also include them?
   + use tfbs encode clustered (in separate model)
* How to handle k562
   +1 unit bin, 1unit flank (10 kb; 20kb)

@@

*Make a bullet pointed list for manuscript
*Apply RF, GBM, SVM (later), MLR using our features
*Finish Methods
*Finish running code applied to 100 iterations of undersampling
*Apply pipeline to K562 cell line
